Blockchain System

### 2021-01-05 papers/execution-model/model.tex
more properties of blockchainstate

\begin{definition}%[Blockchain]
  The \emph{state of a blockchain} is a tuple
  $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current
  time. 
\end{definition}
\clearpage{}
\subsection{Properties of blockchain state transitions}

@@

 \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
   \todo{say something about contract state}
\end{itemize}

\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\EXPRS, \ACCOUNTS, \OPERATIONS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
  \TIME]$ is the state of a blockchain  
  such that
  \begin{itemize}
  \item
    $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK =
    c.\PUK$;
  \end{itemize}
\end{enumerate}
\end{definition}

>>>>

\begin{definition}%[Blockchain]
  The \emph{state of a blockchain} is a tuple
  $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current
  time. 
\end{definition}
\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\EXPRS, \ACCOUNTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
  \TIME]$ is the state of a blockchain  
  such that
  \begin{itemize}
  \item
    $\forall a \in \ACCOUNTS \implies a.\PUK \in \DOM( \MANAGERS)$;
  \end{itemize}
\end{enumerate}
\end{definition}

\clearpage{}
\subsection{Properties of blockchain state transitions}

@@

 \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$
   \todo{say something about contract state}
   \begin{itemize}
   \item for all $\PUH \in \DOM (\CONTRACTORS)$,
     $\CONTRACTORS (\PUH).\CODE = \CONTRACTORS' (\PUH).\CODE$
   \end{itemize}
\end{itemize}

\subsection{Typing related properties}

To describe contracts we associate each public hash to a pair of
types, the parameter type and the storage type.
\begin{align*}
  \Delta & ::= \EmptyEnv \mid \PUH: \TPAIR\ \TYPE\ \TYPE, \Delta
\end{align*}

Define $ \Delta \vdash \CONTRACTORS$ by
\begin{itemize}
\item $\DOM (\Delta) = \DOM (\CONTRACTORS)$
\item $\CONTRACTORS (\PUH).\CODE : \Delta (\PUH) \to FIXEDOUTPUTTYPE$
\item $\CONTRACTORS (\PUH).\STORAGE : \TYPE_s$ where $\Delta (\PUH) =
  \TPAIR\ \TYPE_p\ \TYPE_s$. 
\end{itemize}

Preservation

If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$
and $\Delta \vdash \CONTRACTORS$, \\
then
there is some $\Delta' \supseteq \Delta$ such that $\Delta' \vdash
\CONTRACTORS'$.

Consider a blockchain state  $[\PENDING, \MANAGERS, \CONTRACTORS,
\TIME]$ where $\Delta \vdash \CONTRACTORS$.

For all $\OPH\in\DOM (\PENDING)$,
if  $\PENDING (\OPH) =  \Angle{\OP, \hat\TIME, \STATUS}$
\begin{itemize}
\item if $\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ$, then
  $\PUK, \PUK' \in \DOM (\MANAGERS)$
  \todo{anything else to say here?}
\item if $\OP = \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ$, then
  \begin{itemize}
  \item $\PUH\in\DOM (\CONTRACTORS)$
  \item $\STRING : \TYPE_p$
  \item $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$. 
  \end{itemize}
\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
  \STATUSINCLUDED\ \TIME'$, then
  \todo{what is the right thing to say here? Where do we obtain the
    $\PUH$? How is it related to the $\OPH$?}
